---
---

## Simulation

Streamline the process of executing a model run by defining an R function that runs multiple lines of RNetLogo functions. See the [basic R lesson](https://sesync-ci.github.io/basic-R-lesson/#/slides/functions) to learn about writing functions in R. 

```{r, cache=TRUE, title = "{{ site.handouts[0] }}"}

my_sim <- function(n_wolves){
  NLCommand("setup", "set initial-number-wolves", n_wolves)
  NLDoCommandWhile("any? wolves and any? sheep and ticks < 300", "go")
  ret <- NLReport(reporter = "ticks")
  return(ret)
}

```

```{r}
my_sim(100)
```

What are the input and output of this model? 

===

The `replicate` function makes it easy to run this function multiple times.

```{r}
replicate(n = 5, expr = my_sim(100))
```


===

To run the function using different parameters, create a vector to use with an `lapply()` function

```{r, cache=TRUE, title = "{{ site.handouts[0] }}"}
n_wolves <- seq(100, 250, 50)

res <- lapply(n_wolves, function(x) my_sim(x))
```

```{r}
head(res)
```

===

We can define a function that combines `replicate` and `lapply` to repeat a simulation the same number of times for each value in the range of parameters.

```{r, cache=TRUE, title = "{{ site.handouts[0] }}"}
rep_sim <- function(n_wolves, reps){
  res <- lapply(n_wolves, function(x) replicate(n = reps, expr = my_sim(x)))
  return(res)
}

sim_results <- rep_sim(n_wolves = seq(100, 250, 50), reps = 5)
```

```{r}
head(sim_results)
```

  